On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-06-12 main.tex
Corrections in Theorem 2.2 and the genericity assumptions

\item $W(\pi_i,V(f))$ is either empty or in Noether position for
  $\pi_{i-1}$.
\end{enumerate}
When $\textbf{H}_i(1)$ holds, given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
in $\C^{i-1}$, we further say that $f$ and $\bm \sigma$ satisfy
$\textbf{H}'_i$ if
\begin{enumerate}
\item For any root $\xb$ of 
\[
(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
  X_{i+1}},\dots,{\pa f}/{\pa X_n}),
\]
  the Jacobian matrix of these equations at $\xb$ has full rank $n.$

{\em By point (1) above, we know that there are finitely many solutions 
    to these equations.}
%\item The ideal generated by polynomials $X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
%  X_{i+1}},\dots,{\pa f}/{\pa X_n}$ is
%  radical.
%  
%  {\em By point (2) above, we know that there are finitely many solutions 
%    to these equations.}
\end{enumerate}

@@

\begin{theorem}\label{theo:Hp}
  Suppose that $f$ satisfies $\textbf{H}_i$. Then for  $i=1,\dots,n$, there exists a non-zero
  polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most
  $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
  cancel $\Xi_{i}$, then $f$ and $\bm \sigma$ satisfy $\textbf{H}_i'$.
\end{theorem}
\noindent 
The proof of these theorems occupies the next two sections. Some
related results appear in the literature; for instance, Lemma 5
in~\cite{JeSa10} or Proposition 4.5
in~\cite{SharpEstimatesForTheEffectiveN} are quantitative Noether
position statements. However, Theorem~\ref{theo:gen} does not follow
from these previous results. Indeed, those references would allow us
to quantify when $W(\pi_i,V(f))^\mA$ is in Noether position, whereas
we need to understand when $W(\pi_i,V(f^\mA))$ is. As we pointed out
before, these two sets are in general different.

>>>>

\item $W(\pi_i,V(f))$ is either empty or in Noether position for
  $\pi_{i-1}$.
\end{enumerate}
Given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
in $\C^{i-1}$, we further say that $f$ and $\bm \sigma$ satisfy
$\textbf{H}'_i$ if
\begin{enumerate}
\item For any root $\xb$ of 
\[
(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
  X_{i+1}},\dots,{\pa f}/{\pa X_n}),
\]
  the Jacobian matrix of these equations at $\xb$ has full rank $n.$ 
{\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
  implies that there are finitly many solutions to these equations.}
%\item The ideal generated by polynomials $X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
%  X_{i+1}},\dots,{\pa f}/{\pa X_n}$ is
%  radical.
%  
%  {\em By point (2) above, we know that there are finitely many solutions 
%    to these equations.}
\end{enumerate}

@@

\begin{theorem}\label{theo:Hp}
  For $i=1,\dots,n$, suppose that $f$ satisfies $\textbf{H}_i$, then there exists a non-zero polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
  cancel $\Xi_{i}$, then $f$ and $\bm \sigma$ satisfy $\textbf{H}_i'$.
\end{theorem}
\noindent 
The proof of these theorems occupies the next two sections. Some
related results appear in the literature; for instance, Lemma 5
in~\cite{JeSa10} or Proposition 4.5
in~\cite{SharpEstimatesForTheEffectiveN} are quantitative Noether
position statements. However, Theorem~\ref{theo:gen} does not follow
from these previous results. Indeed, those references would allow us
to quantify when $W(\pi_i,V(f))^\mA$ is in Noether position, whereas
we need to understand when $W(\pi_i,V(f^\mA))$ is. As we pointed out
before, these two sets are in general different.
